Seshadri constants of curve configurations on surfaces

### 2024-03-21 sc-curve-config.tex
Final-version-after-1st-review

Adding over all $i$, we have 
		$$(\triangle) : \quad (L \cdot D)\sum_{i=1}^d b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum_{i=1}^d L\cdot C_i.$$
		By B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$, we obtain
		%\begin{eqnarray*}
		%D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
		%&=& m_{p}(D)\cdot b_i.
		%\end{eqnarray*}
%for each $i$. Summing over all $i$, we get	
		\begin{eqnarray*}
		 D\cdot (C_{1}+ \ldots + C_{d}) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i},
		\end{eqnarray*}
		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
		of $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ and note the following  inequality: 
		\[
		\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D \geq D\cdot C_i.
		\] 
		After adding over all $i=1,...,d$, this leads to the following, 
		\begin{eqnarray*}
			\frac{d^2\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D &\geq&  D\cdot (C_{1}+ \ldots + C_{d}) > \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i} \\
			%\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $\sum b_i > 0$ and $L$ is ample)}.
		\end{eqnarray*}
		This is a contradiction, since $d\geq 4$.
	\end{proof}

@@

The proof of Theorem \ref{main-theorem} can be modified to show that for arrangements
satisfying Assumption \ref{star1} which are not necessarily star arrangements, we still have the following lower and upper bounds for the Seshadri constants.

>>>>

Adding over all $i$, we have 
		$$(\triangle) : \quad (L \cdot D)\sum_{i=1}^d b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum_{i=1}^d L\cdot C_i.$$

  By B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$, we obtain
		%\begin{eqnarray*}
		%D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
		%&=& m_{p}(D)\cdot b_i.
		%\end{eqnarray*}
%for each $i$. Summing over all $i$, we get	
		\begin{eqnarray*}
		 D\cdot (C_{1}+ \ldots + C_{d}) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i},
		\end{eqnarray*}
		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
		of $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ and note the following  inequality: 
		\[
		\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D \geq D\cdot C_i.
		\]

		After adding over all $i=1,...,d$, this leads to the following, 
		\begin{eqnarray*}
			\frac{d^2\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D &\geq&  D\cdot (C_{1}+ \ldots + C_{d}) > \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i} \\
			%\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $\sum b_i > 0$ and $L$ is ample)}.
		\end{eqnarray*}
		This is a contradiction, since $d\geq 4$.
	\end{proof}

@@

The proof of Theorem \ref{main-theorem} can be modified to show that for arrangements
satisfying Assumption \ref{star1}, which are not necessarily star arrangements, we still have the following lower and upper bounds for the Seshadri constants.
